---
title: "Late Invoice Penalty"
author: "Cheeson Lau"
date: "2025-05-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Import the late invoice
```{r}
df_detail <- read.csv("all_late_invoice_detail.csv")
```

Group by Counterparty
```{r}
late_amount_summary <- df_detail %>% 
  group_by(Counterparty) %>% 
  summarise(TotalLateInvoiceAmount = sum(Invoice.Amount)) %>% 
  arrange(desc(TotalLateInvoiceAmount))

late_amount_summary
```

I decide to divided these counterparties into 4 groups. They have different penalty allocation. More amount paid late, more penalty on their credit limit. The amount can be changed if you think it is too much or too little.

Total Late Amount > $100,000 -- Deduct 8%
\$10,000 < Total Late Amount < \$99,999 -- Deduct 6%
\$1,000 < Total Late Amount < $9,999 -- Deduct 4%
Total Late Amount < $999 -- Deduct 2%


Histogram to visualize late invoice amount better.
```{r}
ggplot(late_amount_summary, aes(x = Counterparty, y = TotalLateInvoiceAmount)) +
  geom_bar(stat = "identity", fill = "darkgray") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Total Late Invoice Amount by Counterparty",
       x = "Counterparty",
       y = "Total Late Invoice Amount")
```

